### 2021-03-17 paper.Rmd
Clarification on sectioning.

The classic tour displays work with projections, and interactive systems like GGobi also provide the option of adding sectioning information via linked brushing. Sectioning can be considered as providing complementary information, and in combination with projections we can for example gain insights into the dimensionality of a data structure [@Furnas1994-dz]. Sectioning a high-dimensional space in systematic manner (without interactive selection of data sections) is challenging, since there is a lot of freedom in choosing a section. A new approach is implemented in the slice tour display [@Laa2020-js], which is using the distance of each from the current projection plane (typically placed such that it passes through the data mean) to highlight points that are nearby and fade out points further from the plane.

>>>>

The classic tour displays work with projections, and interactive systems like GGobi also provide the option of adding sectioning information via linked brushing. Sectioning means we select points that fall in a section of the full parameter space, for example for the purpose of highlighting them in a tour display. This often reveals complementary information, and combining sections and projections can for example provide insights into the dimensionality of a data structure [@Furnas1994-dz].

Sectioning a high-dimensional space in systematic manner (without interactive selection of data sections) is challenging, since there is a lot of freedom in choosing a section. One approach is to define sections based on projection planes, we refer to such sections as "slices" of the data. This is implemented in the slice tour display [@Laa2020-js], and uses the orthogonal distance of each data point from the current projection plane (typically placed such that it passes through the data mean) to highlight points that are nearby and fade out points further from the plane.
